s.function for 10 postcodes

### 2025-01-21 src/s_la_per_firm_corrected.Rmd
0595_10

>>>>

## Average ranks websites per firm t and 2012 only: 05 and 95

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only0595_av.png")

  mutate(alpha = ifelse(abs(diff_1st) <= 3.75 | abs(diff_1st) > 253, 1, 0.5)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.5, alpha)) %>%
  mutate(q = ifelse(abs(diff_1st) <= 3.75, "05",
                    ifelse(abs(diff_1st) > 253, "95", "m"))) %>% 
  mutate(q = ifelse(is.na(diff_1st), "m", q)) %>% #filter(rank < 100 & q == "95")
  mutate(label = ifelse(abs(diff_1st) > 253  & q == "95", #& rank < 100
                        LAD21NM, "")) %>% 
  mutate(label.low = ifelse(abs(diff_1st) <= 3.75  & q == "05", #& rank < 100
                        LAD21NM, "")) %>%

  filter(abs(diff_1st) > 253 & rank > 100 & q == "95") %>% distinct(LAD21NM)

  ggplot(aes(year, rank, group = ladcd, alpha=alpha)) +
  geom_bump(aes(colour = q)) + #colour = "red"
  scale_color_manual(values = c("darkorchid3", "orange", "grey70"),
                     breaks = c("05", "95"),
                     labels = c("Stability","Volatility")) + 
  labs(color = "LAD") +
  scale_y_reverse(labels = c(1, 100, 200, 300, 400)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  #theme(legend.position="none") +

  geom_text_repel(aes(x = Inf, label = label), 
                  size = 3, hjust = 0, color = "darkorange3", 
                  max.overlaps = Inf,
                  min.segment.length = Inf,
                  hjust = "left") + # x = 2012 + .1

  geom_text_repel(aes(x = -Inf, label = label.low), 
                  size = 3, hjust = 0, color = "darkorchid4", 
                  max.overlaps = Inf,
                  min.segment.length = Inf,
                  hjust = "left") + # x = 2012 + .1

  scale_x_continuous(NULL, 
                     #limits = c(1998, 2010), 
                     breaks=c(1998, 2010),
                     labels = c("1996-98","2010-12")) +
  guides(alpha = "none")

ggsave(out.path)
```

```{r}
path.in <- paste0(path, "/outputs/s/s_la_per_firm.csv")

latecomers <- c("Halton", "Blackpool", "Rutland", "Torbay", "Isles of Scilly", "North Devon", "Gosport", "Thanet", "Na h-Eileanan Siar", "Conwy")

earlyadopters <- c("Slough", "Three Rivers", "Epsom and Ewell", "City of London", "Hillingdon", "Hounslow", "Kensington and Chelsea", "Kingston upon Thames", "Richmond upon Thames", "Wandsworth")

la.df <- read_csv(path.in)

early <- la.df %>% filter(LAD21NM %in% earlyadopters) %>% 
  dplyr::select(LAD21NM, estimate, fast) %>% 
  mutate(estimate = round(estimate, 1)) %>% 
  mutate('early/late' = "early adopting") %>% 
  rename(LAD = LAD21NM)

late <- la.df %>% filter(LAD21NM %in% latecomers) %>% 
  dplyr::select(LAD21NM, estimate, fast) %>% 
  mutate(estimate = round(estimate, 1)) %>% 
  mutate('early/late' = "late coming") %>% 
  rename(LAD = LAD21NM)

df.late.early <- bind_rows(late, early)

path.out <- paste0(path, "/outputs/ranks/late_early.csv")
write_csv(df.late.early, path.out)

# stargazer(df.late.early[1:20,],
#           type = 'text', 
#           summary = FALSE)
```

### 2025-01-21 src/s_la_per_firm_corrected_10.Rmd

>>>>

## Average ranks websites per firm t and 2012 only: 05 and 95

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only0595_av_10.png")

  # ungroup() %>% summarise(q = quantile(abs(diff_1st), .05, na.rm = T))
  # q.95 = 194.5, q.9 = 162.5, q.1 = 10.5, q.05 = 5. **abs()**

  mutate(alpha = ifelse(abs(diff_1st) <= 5 | abs(diff_1st) > 194.5, 1, 0.5)) %>% 
  mutate(alpha = ifelse(is.na(diff_1st), 0.5, alpha)) %>%

  mutate(q = ifelse(abs(diff_1st) <= 5, "05",
                    ifelse(abs(diff_1st) > 194.5, "95", "m"))) %>% 
  mutate(q = ifelse(is.na(diff_1st), "m", q)) %>%

  ggplot(aes(year, rank, group = ladcd, alpha=alpha)) +
  geom_bump(aes(colour = q)) + #colour = "red"
  scale_color_manual(values = c("darkorchid3", "orange", "grey70"),
                     breaks = c("05", "95"),
                     labels = c("Stability","Volatility")) + 
  labs(color = "LAD") +
  scale_y_reverse(labels = c(1, 100, 200, 300, 400)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  #theme(legend.position="none") +
  scale_x_continuous(NULL, 
                     #limits = c(1998, 2010), 
                     breaks=c(1998, 2010),
                     labels = c("1996-98","2010-12")) +
  guides(alpha = "none")

ggsave(out.path)
```
